### 2022-05-13 manuscript.Rmd
Fine-tune tables

  \addORCIDlink{Anne-Sophie Kieslinger}{https://orcid.org/0000-0001-9240-4077}

@@

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \renewcommand{\arraystretch}{0.59}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

# Options for MCMC sampling when fitting Bayesian multilevel models
n_iter <- 4000 # Posterior samples per chain, including `n_warmup`
n_warmup <- 1000 # Warmup samples per chain
n_chains <- 4 # Number of (parallel) chains
seed <- 1234 # Random seed to make the results reproducible

@@

\scriptsize

@@

\normalsize

@@

\scriptsize

@@

## Effect size measures

@@

We synthesized the effect sizes and their sampling variances using a Bayesian multilevel model. This model had three levels, with infant participants nested in experiments and experiments nested in articles [@vandennoortgate2013]. We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for all standard deviations [@williams2018]. A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 5). For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect size measures above). For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges' $g$) between male infants' mental rotation performance and female infants' mental rotation performance, weighted by its standard error. All Bayesian models were fitted using the brms package (Version `r packageVersion("brms")`) [@burkner2017; @burkner2018] in R (Version `r packageVersion("base")`) [@rcoreteam2021] and the Stan language (Version `r packageVersion("rstan")`) [@standevelopmentteam2022]. Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r formatC(n_iter, big.mark = ",")` draws (including `r formatC(n_warmup, big.mark = ",")` warm-up draws) from the posterior distribution. To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig. 2) [@vehtari2021]. For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].

@@

@@

>>>>

  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}

@@

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

# Options for MCMC sampling when fitting Bayesian multilevel models
n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
n_warmup <- 2000 # Warmup samples per chain
n_chains <- 4 # Number of (parallel) chains
seed <- 1234 # Random seed to make the results reproducible

@@

\newpage
\renewcommand{\arraystretch}{2}
\singlespacing
\scriptsize

@@

\doublespacing
\normalsize

@@

\singlespacing
\scriptsize

@@

## Effect measures

@@

We synthesized the effect sizes and their sampling variances using a Bayesian multilevel model. This model had three levels, with infant participants nested in experiments and experiments nested in articles [@vandennoortgate2013]. We used a weakly-informative $\mathcal{N}(0,1)$ (normal) prior for the meta-analytic effect size and a weakly-informative $\mathcal{HC}(0,0.3)$ (half-Cauchy) prior for all standard deviations [@williams2018]. A prior sensitivity analysis indicated that making these priors either more informative or less informative did not change the meta-analytic results (Supplementary Table 5). For the meta-analysis of mental rotation performance, the dependent variable was the standardized mean difference (Hedges' $g$) between the novel and familiar rotation condition, weighted by its standard error (see Effect measures above). For the meta-analysis of gender differences, the dependent variable was the standardized mean difference (Hedges' $g$) between male infants' mental rotation performance and female infants' mental rotation performance, weighted by its standard error. All Bayesian models were fitted using the brms package (Version `r packageVersion("brms")`) [@burkner2017; @burkner2018] in R (Version `r packageVersion("base")`) [@rcoreteam2021] and the Stan language (Version `r packageVersion("rstan")`) [@standevelopmentteam2022]. Markov Chain Monte Carlo (MCMC) sampling was used with four parallel chains, each sampling `r formatC(n_iter, big.mark = ",")` draws (including `r formatC(n_warmup, big.mark = ",")` warm-up draws) from the posterior distribution. To verify the convergence of the Markov chains, we examined rank plots as well as the $R_\text{hat}$ and $N_\text{eff}$ statistics (Supplementary Fig. 2) [@vehtari2021]. For reporting, the credible interval (CrI) for each model parameter was computed as the 95% equal-tailed interval (ETI) of its posterior distribution, although replacing this with the 95% highest density interval (HDI) yielded highly similar results [@kruschke2015].

@@

\newpage
\nolinenumbers

@@

\newpage
\linenumbers

### 2022-05-13 supplement.Rmd
Fine-tune tables

```{r, tabs1, include=TRUE}
# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = as.integer(sample_size),
    `Females` = as.integer(round(female_percent * sample_size)),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) -> tabs1

@@

@@

@@

```{r, tabs4, include=TRUE}
# Read PRISMA checklist from file
tab_prisma <- read_csv(
  here(data_dir, "prisma_checklist.csv"),
  col_types = "ccc"
)

# Display the table
apa_table(
  tab_prisma,
  caption = "PRISMA 2020 checklist",
  font_size = "scriptsize",
  align = "lrl",
)
```

>>>>

\singlespacing
\renewcommand{\arraystretch}{0.97}

```{r, tabs1, include=TRUE}
# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = as.integer(sample_size),
    Females = as.integer(round(female_percent * sample_size)),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) %>%
  mutate(
    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
  ) -> tabs1

@@

\renewcommand{\arraystretch}{1.10}

@@

\renewcommand{\arraystretch}{0.97}

@@

\renewcommand{\arraystretch}{1.30}

```{r, tabs4, include=TRUE}
# Read PRISMA checklist from file
tab_prisma <- read_csv(
  here(data_dir, "prisma_checklist.csv"),
  col_types = "ccc", na = character()
)

# Display the table
apa_table(
  tab_prisma,
  caption = "PRISMA 2020 checklist", font_size = "scriptsize",
  landscape = TRUE, align = "p{1.5cm}p{2.5cm}p{1cm}p{12cm}p{5.5cm}",
)
```
